---
title: Preliminary Modelling for the Stock Assessment of Shortfin Mako Shark, Isurus
  oxyrinchus
author: A.E. Nieblas1, S. Bonhommeau2, A. Bennicci1, E. Anello1, E. Blondel1, A. Ellenbroek1,
  M. Taconet1, J. Barde3, P. de Bruyn4, F. Fiorellato4. Lauren Nelson4, Emmanuel Chassot4,
  Dan Fu4
date: "8/19/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
### If JABBA is no installed on your computer install it with:
# library(devtools)
# install_github("jabbamodel/JABBA")
### see more details at https://github.com/jabbamodel/JABBA
p_load(JABBA, plyr, reshape2, ggplot2, viridis, RColorBrewer, ggsci)
```

## Abstract
This is the abstract


## Introduction
This is the introduction

## Materials and Methods
This is the M&M

### Fisheries data
#### Catch time-series
IOTC data, reconstructed...


```{r, echo=FALSE}
NC <- read.csv("data/IOTC-2020-DATASETS-NCDB_080420.csv", header = T, stringsAsFactors = F)
SMANC <- NC[which(NC$SpCde=="SMA"),]
colnames(SMANC)[8]  <- "Year"
colnames(SMANC)[29] <- "Catch"
SMANC$Catch <- as.numeric(as.character(SMANC$Catch))
SMANCYearGear <- ddply(SMANC, .(GrCde, Year), function(x) sum(x$Catch, na.rm=T))
#SMANCYearGear <- rbind(SMANCYearGear, data.frame(GrCde="Total", ddply(SMANC, .(Year), function(x) sum(x$Catch, na.rm=T))))
colnames(SMANCYearGear)[1] <- "Gear"
colnames(SMANCYearGear)[3] <- "Catch"
nb.cols <- length(unique(SMANCYearGear$Gear))
mycolors <- colorRampPalette(brewer.pal(12, "Paired"))(nb.cols)
p <- ggplot(SMANCYearGear, aes(x=Year, y=Catch, fill=Gear))+
  geom_area()+
  scale_fill_manual(values=mycolors)#scale_fill_lancet() #scale_fill_brewer(palette = brewer.pal(14, "RdYlBu")) #scale_fill_viridis(discrete = TRUE)
p+theme_light()
```
#### Map of catch and effort by fleet by decades

### Catch per unit of effort data

#### Size frequencies

### Biological data
- Growth (VB parameters)
- Intrinsic growth rate (see appendix A)
- Lifespan
- ...
Make a table

### Stock assessment model

#### CMSY

#### ELEFAN

#### Yield per recruit

#### JABBA




## Results
These are the results

## Discussion
This is the discussion

## Appendix

### Appendix A: Prior elicitation for the intrinsic population growth rate





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
