---
title: Preliminary Modelling for the Stock Assessment of Shortfin Mako Shark, Isurus
  oxyrinchus
author: A.E. Nieblas1, S. Bonhommeau2, A. Bennicci1, E. Anello1, E. Blondel1, A. Ellenbroek1,
  M. Taconet1, J. Barde3, P. de Bruyn4, F. Fiorellato4. Lauren Nelson4, Emmanuel Chassot4,
  Dan Fu4
date: "8/19/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract
This is the abstract


## Introduction
This is the introduction

## Materials and Methods
This is the M&M

### Fisheries data
#### Catch time-series
IOTC data, reconstructed...

#### Map of catch and effort by fleet by decades

### Catch per unit of effort data

#### Size frequencies

### Biological data
- Growth (VB parameters)
- Intrinsic growth rate (see appendix A)
- Lifespan
- ...
Make a table

### Stock assessment model

#### CMSY

#### ELEFAN

#### Yield per recruit

#### JABBA




## Results
These are the results

## Discussion
This is the discussion

## Appendix

### Appendix A: Prior elicitation for the intrinsic population growth rate





```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
