---
title: |
  Preliminary Modelling for the Stock Assessment of Shortfin Mako Shark, Isurus oxyrinchus
subtitle: |
  Showcasing the FAO SDG 14.4.1 Stock Monitoring Tool by applying one of its data-limited methods, CMSY, and comparing its results to JABBA.
author: 
  - A.E. Nieblas:
      email: anne.nieblas@fao.org
      institute: [FAO]
      correspondence: true
  - S. Bonhommeau:
      email: sylvain.bonhommeau@ifremer.fr
      institute: [IFREMERDOI]
      correspondence: false
  - A. Bennicci:
      email: bennicci@fao.org
      institute: [FAO]
      correspondence: false
  - E. Anello:
      email: enrico.anelo@fao.org
      institute: [FAO]
      correspondence: false    
  - E. Blondel:
      email: emmanuel.blondel@fao.org
      institute: [FAO]
      correspondence: false
  - A. Ellenbroek:
      email: anton.ellenbroek@fao.org
      institute: [FAO]
      correspondence: false
  - J. Barde:
      email: julien.barde@ird.fr
      institute: [IRD]
      correspondence: false
  - P. de Bruyn:
      email: paul.de.bruyn@fao.org
      institute: [IOTC]
      correspondence: false
  - F. Fiorellato:
      email: fabio.fiorellato@fao.org
      institute: [IOTC]
      correspondence: false
  - L Nelson:
      email: alauren.nelson@fao.org
      institute: [IOTC]
      correspondence: false
  - E. Chassot:
      email: emmanuel.chassot@fao.org
      institute: [IOTC]
      correspondence: false  
  - D. Fu: 
      email: dan.fu@fao.org
      institute: [IOTC]
      correspondence: false
institute:
  - FAO: Food and Agriculture Organization
  - IFREMERDOI: Ifremer DOI
  - IOTC: Indian Ocean Tuna Commission
abstract: |
date: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
### If JABBA is no installed on your computer install it with:
# library(devtools)
# install_github("jabbamodel/JABBA")
### see more details at https://github.com/jabbamodel/JABBA
p_load(JABBA, plyr, reshape2, ggplot2, viridis, RColorBrewer, ggsci)
```

## Abstract
This is the abstract
Line added
lsdjfalsjd
jkjgkgjf syl
tata

## Introduction
This is the introduction

## Materials and Methods
This is the M&M

### Fisheries data
#### Catch time-series
IOTC data, reconstructed...


```{r, echo=FALSE}
NC <- read.csv("data/IOTC-2020-DATASETS-NCDB_080420.csv", header = T, stringsAsFactors = F)
SMANC <- NC[which(NC$SpCde=="SMA"),]
colnames(SMANC)[8]  <- "Year"
colnames(SMANC)[29] <- "Catch"
SMANC$Catch <- as.numeric(as.character(SMANC$Catch))
SMANCYearGear <- ddply(SMANC, .(GrCde, Year), function(x) sum(x$Catch, na.rm=T))
#SMANCYearGear <- rbind(SMANCYearGear, data.frame(GrCde="Total", ddply(SMANC, .(Year), function(x) sum(x$Catch, na.rm=T))))
colnames(SMANCYearGear)[1] <- "Gear"
colnames(SMANCYearGear)[3] <- "Catch"
nb.cols <- length(unique(SMANCYearGear$Gear))
mycolors <- colorRampPalette(brewer.pal(12, "Paired"))(nb.cols)
p <- ggplot(SMANCYearGear, aes(x=Year, y=Catch, fill=Gear))+
  geom_area()+
  scale_fill_manual(values=mycolors)#scale_fill_lancet() #scale_fill_brewer(palette = brewer.pal(14, "RdYlBu")) #scale_fill_viridis(discrete = TRUE)
p+theme_light()
```
#### Map of catch and effort by fleet by decades

```{r, echo=FALSE}
CECoastal <- read.csv("data/IOTC-2019-DATASETS-CECoastal.csv", header = T, stringsAsFactors = F)
CECoastalmelt <- melt(CECoastal, id.vars = colnames(CECoastal)[1:11])
CESurface <- read.csv("data/IOTC-2019-DATASETS-CESurface.csv", header = T, stringsAsFactors = F)
CESurfacemelt <- melt(CESurface, id.vars = colnames(CESurface)[1:11])
CELongline <- read.csv("data/IOTC-2019-DATASETS-CESurface.csv", header = T, stringsAsFactors = F)
CELonglinemelt <- melt(CELongline, id.vars = colnames(CELongline)[1:11])
CETot <- rbind(CECoastalmelt, CELonglinemelt, CESurfacemelt)
CESMATot <- CETot[which(CETot$variable=="SMA.MT"),]

SMANC <- NC[which(NC$SpCde=="SMA"),]
colnames(SMANC)[8]  <- "Year"
colnames(SMANC)[29] <- "Catch"
SMANC$Catch <- as.numeric(as.character(SMANC$Catch))
SMANCYearGear <- ddply(SMANC, .(GrCde, Year), function(x) sum(x$Catch, na.rm=T))
#SMANCYearGear <- rbind(SMANCYearGear, data.frame(GrCde="Total", ddply(SMANC, .(Year), function(x) sum(x$Catch, na.rm=T))))
colnames(SMANCYearGear)[1] <- "Gear"
colnames(SMANCYearGear)[3] <- "Catch"
nb.cols <- length(unique(SMANCYearGear$Gear))
mycolors <- colorRampPalette(brewer.pal(12, "Paired"))(nb.cols)
p <- ggplot(SMANCYearGear, aes(x=Year, y=Catch, fill=Gear))+
  geom_area()+
  scale_fill_manual(values=mycolors)#scale_fill_lancet() #scale_fill_brewer(palette = brewer.pal(14, "RdYlBu")) #scale_fill_viridis(discrete = TRUE)
p+theme_light()
```

### Catch per unit of effort data

#### Size frequencies

### Biological data
- Growth (VB parameters)
- Intrinsic growth rate (see appendix A)
- Lifespan
- ...
Make a table

### Stock assessment model

#### CMSY

#### ELEFAN

#### Yield per recruit

#### JABBA




## Results
These are the results

## Discussion
This is the discussion

## Appendix

### Appendix A: Prior elicitation for the intrinsic population growth rate





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
